---
title: "My first markdown"
author: Qianran(Zoe) Wang
output: html_document
---

  >## What is Markdown
  >### R markdown is the integration of R code with markdown
  >### Allows one to create documents that interweave R code with ordinary text R code is evaluated as part of the processing of the markdown
  >### Results from R code are inserted into markdown document

`hello` hello

  >$H_0$
  
*Italic*

**Bold**

## This is section
Let's load some data.

include = False hide everything include in the console
echo = False only hide the code

```{r}
library(datasets)
data("airquality")
summary(airquality)
```

Here's a paris plots of the data

```{r}
pairs(airquality)
```

Here's a regression model of ozone on some predictors.

```{r echo=FALSE}
fit <- lm(Ozone ~ Solar.R + Wind + Temp, data = airquality)
summary(fit)
```

Here's an unordered list

* **race** is Here's item one
    * first sub
    * second sub
* **owngun** Item 2

Ordered list

1. first item

2. second item

Math notation putting:

  >$H_0$
  
  >$H_1$

